---
title: "Lab 03 - Nobel laureates"
author: "Cailey Fay"
date: "10.7.25"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r summarize}
nrow(nobel)
ncol(nobel)
#There are 26 variables and 935 observations. 
```

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

```{r data frames}
nobel_living <-nobel %>%
    filter(!is.na(died_date))

nobel_living %>%
  select(died_date, gender, country)

#not quite what you are looking for, need to filter out the observations that arent people, and the people who arent affiliated with a country
```
```{r take two}
new_nobel <-nobel %>%
    filter(!is.na(died_date),!is.na(gender), !is.na(country))

new_nobel%>%
  select(died_date, gender, country)
  nrow(new_nobel)
```
### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
